Data Analysis

### 2022-06-17 03.data_analysis.Rmd
update the things

```{r}
library(dplyr)
library(bib2df)
library(rio)
library(tidyr)
library(ggplot2)
library(nlme)
library(RColorBrewer)
library(countrycode)
library(maps)
library(MOTE)
current_year <- 2022
#### fix sau chins paper #### https://osf.io/gq92w/ 
```

@@

>>>>

```{r}
library(dplyr)
library(bib2df)
library(rio)
library(tidyr)
library(ggplot2)
library(nlme)
library(RColorBrewer)
library(countrycode)
library(maps)
library(MOTE)
current_year <- 2022

## fixes
## update sau chins paper with new list https://osf.io/gq92w/ 
## make list of OSC
## add Many Primates list 
## update Dorison et al.

## double check each publication for proper year and journal
## look at merged id and incorrect ids 
```

@@

- test the merge

```{r}
merged_test <- 
  long_bib %>% 
  select(first, last, TITLE) %>% 
  full_join(
    # note this isn't perfect ... will have to make sure all versions 
    # get matched 
    (id_list %>% select(first, last, full, ORCID, scholar)), 
    by = c("first" = "first", "last" = "last") 
  )

# if full name is blank, then the person is not in our id_list
merged_test %>% 
  filter(!duplicated(merged_test %>% select(first, last))) %>% 
  filter(is.na(full)) %>% 
  export("missing_id_list.xlsx")

# if no title they are in id_list but aren't merging correctly 
merged_test %>% 
  filter(is.na(TITLE)) %>% 
  export("incorrect_id_list.xlsx")
```
